\addcontentsline{toc}{chapter}{Список использованных источников}

\begin{thebibliography}{99}

\bibitem{kleppmann}
\textit{Клеппман М.} Высоконагруженные приложения. Программирование, масштабирование и поддержка. --- СПб.: Питер, 2018. --- 640 с.

\bibitem{tanenbaum}
\textit{Таненбаум Э., ван Стеен М.} Распределенные системы. Принципы и парадигмы. --- СПб.: Питер, 2013. --- 877 с.

\bibitem{go_lang}
\textit{Донован А., Керниган Б.} Язык программирования Go. --- М.: Вильямс, 2016. --- 432 с.

\bibitem{raft_original}
\textit{Ongaro D., Ousterhout J.} In Search of an Understandable Consensus Algorithm // Proceedings of the 2014 USENIX Annual Technical Conference. --- Philadelphia, PA, 2014. --- P. 305-320.

\bibitem{raft_dissertation}
\textit{Ongaro D.} Consensus: Bridging Theory and Practice. PhD Dissertation. --- Stanford University, 2014.

\bibitem{flp_theorem}
\textit{Fischer M., Lynch N., Paterson M.} Impossibility of Distributed Consensus with One Faulty Process // Journal of the ACM. --- 1985. --- Vol. 32, No. 2. --- P. 374-382.

\bibitem{cap_theorem}
\textit{Gilbert S., Lynch N.} Brewer's conjecture and the feasibility of consistent, available, partition-tolerant web services // ACM SIGACT News. --- 2002. --- Vol. 33, No. 2. --- P. 51-59.

\bibitem{paxos_simple}
\textit{Lamport L.} Paxos Made Simple // ACM SIGACT News. --- 2001. --- Vol. 32, No. 4. --- P. 18-25.

\bibitem{lynch_book}
\textit{Lynch N. A.} Distributed Algorithms. --- San Francisco: Morgan Kaufmann Publishers Inc., 1996. --- 872 p.

\bibitem{zookeeper}
\textit{Junqueira F., Reed B.} ZooKeeper: Distributed Process Coordination. --- O'Reilly Media, 2013.

\bibitem{linearizability}
\textit{Herlihy M., Wing J.} Linearizability: A Correctness Condition for Concurrent Objects // ACM Transactions on Programming Languages and Systems. --- 1990. --- Vol. 12, No. 3. --- P. 463-492.

\bibitem{etcd_docs}
\textit{etcd documentation.} Distributed reliable key-value store, Raft-based design notes. --- Режим доступа: \url{https://etcd.io/docs/} (дата обращения: 01.05.2026).

\bibitem{pebble}
\textit{Cockroach Labs.} Pebble: an embeddable, high-performance, key-value store for Go. --- Режим доступа: \url{https://github.com/cockroachdb/pebble} (дата обращения: 01.05.2026).

\bibitem{leveldb}
\textit{Google.} LevelDB: a fast persistent key-value store. --- Режим доступа: \url{https://github.com/google/leveldb} (дата обращения: 01.05.2026).

\bibitem{jepsen}
\textit{Kingsbury K.} Jepsen: distributed systems safety analysis. --- Режим доступа: \url{https://jepsen.io} (дата обращения: 01.05.2026).

\end{thebibliography}
